% !TeX encoding = ISO-8859-1

\chapter*{Abstract}

Communication is fundamental in social interaction and enables integration and exchange. However, there are people with some functional diversities that affect their verbal communication and they must to use augmentative and alternative communication systems (SAACS) like pictograms that gives support them in communication
Not everyone understands communication with SAACS and this prevents the people who need them to communicate to have an effective communication, as simple as it could be what they want to say.

For that reason, It´s necessary create tools that allows people with some kind of discapacity to integrate in the society and improve their quality of life.

In this final degree project, we have developed a web application to help people with difficulties in communication, this application translates texts written with pictograms to written text in natural language, more specifically in Spanish. At present, there is no application that makes a translation from pictogram to text, for that our project can help to cover that gap.
In addition, the application has been implemented using a component-based design, which allows other developers to integrate any of our independent components into their applications.
Finally, we have made an evaluation for check the correctness of the translations made by our application and the results obtained are quite encouraging although there is still a lot of room for improvement. We can affirm that with the application developed in this project, that have established a solid foundation to continue working to improve coverage and correction of translated texts.

\section*{Keywords}

\begin{itemize}
    \item Pictogram.
    \item Aplication web.
    \item Natural Language Generation.
    \item Web services.
    \item ARAASAC.
\end{itemize}

\clearpage  




 
\section*{Palabras clave}
   


   